### 2019-09-15 reports/thesis/book.tex
Revise

\chapter{Conclusion}
\label{chapter6}
To summarise the thesis, Figure \ref{fig:evaluation_flowchart} shows a flowchart of the process of the experiment. A test sample was designed using a CAD model and was manufactured with purposefully designed voids. Replicate x-ray projections were taken of the test sample with voids as well as a simulation of that projection without the voids using \emph{aRTist}. The obtained projections was used to help align the simulated projection. The aim of the experiment was to develop a statistical method to detect these designed voids.

@@

Shading correction was required to remove spot and panel effects from the obtained projections. This was done by using the greyscale projections from a number of powers of the x-ray tube. By assuming each pixel has a linear response to the power, a linear regression was used. This is discussed in Chapter \ref{chapter2}.

In Chapter \ref{chapter3}, it was attempted to fit a compound Poisson distributed onto the grey values of a projection to quantify the noise. Unfortunately, the model suffered from identifiability issues for high photon counts. However, it was found that the grey value variance has a linear relationship with the grey value. In Chapter \ref{chapter4}, various GLM were fitted onto the variance-mean data and it was verified a linear relationship is a good model. The model was used as a tool to predict the variance of a grey value.

In Chapter \ref{chapter5}, the replicated projections were split into two. 19 randomly selected projections were used for the variance-mean model to fit onto. The remaining projection was compared with the simulated projection under the face of uncertainty. The uncertainty was predicted using the variance-mean model. Inference was done on the test statistics, one for each pixel in a projection. Unfortunately, the simulation was not perfect which led to model misspecification, thus false positives. The empirical null filter was developed and used to smooth the test statistics. This allows the inference to pick out areas which are unusual and unlike its neighbours. The filtered test statistics were converted to $p$-values so that hypothesis testing can be done to detect the voids.

In the ABS test sample, voids of the order of millimetres were detectable using this method. However, for the titanium test sample, the voids were undetectable due to dominating edge effects. The reason for this is unknown. It was speculated that the main source of error was from the simulated projection not being quite pixel-perfect aligned causing model misspecification at the edges. Therefore, the method was unable to distinguish disagreement due to model misspecification or a void. This method could be improved if \emph{aRTist} was integrated into it. For example, the simulated projection could be realigned to minimise the number of positives. This will help eliminate sources of error due to \emph{aRTist}. A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Repeating the experiment using difficult angles may indicate weaknesses from using a singular angle. Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle.

The experiment could be improved if the location of the defects were known in the projection. This would allow identifying which positives are true and false positives so that the analysis can be quantified using a ROC curve.

This thesis is a contribution to real-time quality control for additive manufacturing. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. By using fewer projections, quality control can be faster which advances the development and increase the scope of applications of additive manufacturing.

>>>>

\chapter{Conclusion}
\label{chapter6}
To summarise the thesis, Figure \ref{fig:evaluation_flowchart} shows a flowchart of the process of the experiment. A test sample was designed using a CAD model and was manufactured with purposefully designed voids. Replicate x-ray projections were taken of the test sample with voids as well as a simulation of that projection without the voids using \emph{aRTist}. The obtained projections were used to help align the simulated projection. The experiment aimed to develop a statistical method to detect the designed voids.

@@

Shading correction was required to remove spot and panel effects from the obtained projections. This was done by using the greyscale projections at different exposures. By assuming each pixel has a linear response to the power of the x-ray tube, a linear regression was used. This is discussed in Chapter \ref{chapter2}.

In Chapter \ref{chapter3}, it was attempted to fit a compound Poisson distribution onto the grey values of a projection to quantify the noise. Unfortunately, the model suffered from identifiability issues for high photon counts. However, it was found that the grey value variance has a linear relationship with the grey value. In Chapter \ref{chapter4}, various GLM were fitted onto the variance-mean data and it was verified a linear relationship is a good model. The model was used as a tool to predict the variance of a grey value.

In Chapter \ref{chapter5}, the replicated projections were split into two. 19 randomly selected projections were used for the variance-mean model to fit onto. The remaining projection was compared with the simulated projection in the face of uncertainty. The uncertainty was predicted using the variance-mean model. Hypothesis testing was done on the test statistics, one for each pixel in a projection. Unfortunately, the simulation was not perfect which led to model misspecification, thus, false positives. The empirical null filter was developed and used to smooth the test statistics. This allows the hypotheses test to pick out areas which are unusual and unlike its neighbours. The filtered test statistics were converted to $p$-values so that hypotheses testing can be done to detect the voids.

In the ABS test sample, voids in the order of millimetres were detectable using this method. However, for the titanium test sample, the voids were undetectable due to dominating edge effects. The reason for this is unknown. It was speculated that the main source of error was from the simulated projection not being quite pixel-perfect aligned causing model misspecification at the edges. Therefore, the method was unable to distinguish disagreement due to model misspecification or a void. This method could be improved if \emph{aRTist} was integrated into it. For example, the simulated projection could be realigned to minimise the number of positives. This will help eliminate sources of error due to \emph{aRTist}. A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Defect detection can be tough if a difficult projection angle was used. Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle.

The inference could be improved if the location of the defects were known in the projection. This would allow identifying which positives are true and false positives so that the analysis can be quantified using a ROC curve.

This thesis is a contribution to real-time quality control for additive manufacturing. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of additive manufacturing.
